### 2023-08-18 paper/paper-papaja.Rmd
word count added

---
title             : "Illusory Implications: Evidence that mere exposure to ideas can induce beliefs"
shorttitle        : "Illusory implications"

@@

keywords          : "Illusory truth; Metacognition; Cognitive Psychology; Misinformation"
wordcount         : "X"

>>>>

---
title             : "Illusory Implications: Mere exposure to ideas can induce beliefs"
shorttitle        : "Illusory implications"

@@

keywords          : "Illusory truth; Metacognition; Cognitive Psychology; Misinformation"
wordcount         : "4929"
